Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Add to AL geometry diagram caption

    \caption{Actuator line geometry. Filled circles indicate geometry points
        whereas squares indicate actuator line element locations.}

>>>>

    \caption{Actuator line geometry. Filled circles indicate points where
    geometry is defined whereas squares indicate actuator line element
    quarter-chord locations. Chord mount offset is defined as the distance from
    an element's leading edge to each geometry point in chord lengths, which is
    0.5 for both turbines in this study.}
